---
title: "Visualization covid19italy with Choropleth Maps "
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{geospatial_visualization}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  message=FALSE, 
  warning=FALSE,
  fig.height=8, 
  fig.width=8,
  collapse = TRUE,
  comment = "#>"
)
```


The goal of this vignette is to demonstrate methods for creating choropleth maps for the covid19 cases in Italy by province and region. We will use the [rnaturalearth](https://docs.ropensci.org/rnaturalearth/) package to extract the geometry spital data of Italy, and [mapview](https://r-spatial.github.io/mapview/index.html), [ggplot2](https://ggplot2.tidyverse.org/index.html), and [plotly](https://plotly.com/r/) packages to create interactive choropleth maps of Italy province and regions.




```{r setup}
library(covid19italy)
library(rnaturalearth)
library(dplyr)
library(mapview)
```


## Getting the geometry spital data

The `ne_state` function from the rnaturalearth package returns the geometry spital data of Italy's province. We will set the return class to `sf` (Simple Features) object:

```{r}
italy_map <- ne_states(country = "Italy", returnclass = "sf") 

str(italy_map)
```

The function returns many features, such as a different naming convention. However, for the purpose of this vignette, we will only need the following columns:

* `name` - the province name
* `region` - the region name
* `geometry` - the geometry spital data of the provinces


```{r fig.height=8, fig.width=8}
italy_map <- italy_map %>% 
  select(province = name, region, geometry) 

head(italy_map)
```

The `italy_map` object, as it is, can now use to create a choropleth map plot for the province level. To get a similar object to the regional level, we will use the **dplyr** package to group the data by the `region` column. This will automatically will group the **geometry** objects of the `italy_map` to the region level:

```{r}
italy_map_region <- italy_map %>%
  group_by(region) %>%
  summarise(n = n())

head(italy_map_region)
```

Note that since we had to feed some variable to the `summarise` function, we used the n function as a dummy variable.

Now that we have one object for the province level and one for the regional level, we can start to plot them.

## Choropleth maps with mapview package

```{r}
italy_map %>% 
  left_join(italy_province %>% 
                                 filter(date == max(date)) %>%
                                 select(province = province_spatial, total_cases), 
                               by = "province") %>%
  mapview(zcol = "total_cases")
```



```{r}
italy_map_region %>% 
  
  left_join(italy_region %>% 
                                 filter(date == max(date)) %>%
                                 select(region = region_spatial, total_tests), 
                               by = "region") %>%
  select(-n) %>%
  mapview(zcol = "total_tests")
```
```






